Plant Trait Imputation

### 2024-04-25 code/L1/L1_P4_TropicalAndes_plant_imputetraits.Rmd
add catch and delay to taxize code retriving family and genus information for species from ncbi, fill in NAs of original dataframe and get list of species still missing family info

  # Loop through each species name in the chunk and retrieve taxonomic information
  for (species_name in chunk_species_names) {
    # Add a delay of 1 second between consecutive API requests
    Sys.sleep(1)

    # Make API request to retrieve taxonomic information
    taxon_info <- tax_name(species_name, get = c("genus", "family"), db = "both")

    # Store taxonomic information for the species in the list
    chunk_taxonomic_info[[species_name]] <- data.frame(Species = species_name, 
                                                       Genus = taxon_info$genus, 
                                                       Family = taxon_info$family)
  }

@@

# Define the chunk size
chunk_size <- 100  # Adjust the chunk size as needed

@@

  # Append taxonomic information for the chunk to the list
  all_taxonomic_info <- c(all_taxonomic_info, list(chunk_taxonomic_info))
}

@@

>>>>

  # Loop through each species name in the chunk and retrieve taxonomic information
  for (species_name in chunk_species_names) {
    tryCatch({
      # Add a delay between consecutive API requests
      Sys.sleep(1)

      # Make API request to retrieve taxonomic information
      taxon_info <- tax_name(species_name, get = c("genus", "family"), db = "ncbi")

      # Store taxonomic information for the species in the list
      chunk_taxonomic_info[[species_name]] <- data.frame(Species = species_name, 
                                                         Genus = taxon_info$genus, 
                                                         Family = taxon_info$family)
    }, error = function(e) {
      # Print error message
      cat("Error retrieving taxonomic information for", species_name, ":", conditionMessage(e), "\n")
    })
  }

@@

# Define the chunk size
chunk_size <- 300 # Adjust the chunk size as needed

@@

  # Append taxonomic information for the chunk to the list
  all_taxonomic_info <- c(all_taxonomic_info, list(chunk_taxonomic_info))

  # Add a delay 
  Sys.sleep(5)
}

@@

```{r}
# remove duplicates
taxonomic_df <- distinct(taxonomic_df)
# rename column to family, genus, species
taxonomic_df <- taxonomic_df %>%
  rename(family = Family,
         genus = Genus,
         species = Species)
```

```{r}
# add to species dataframe
na_species_df_2 <- na_species_df %>%
  mutate(family = coalesce(family, taxonomic_df$family),
         genus = coalesce(genus, taxonomic_df$genus))

# retrieve list of species without family & genus information
species_no_family_2 <- na_species_df_2 %>%
  filter(is.na(family) | family == "") %>%
  select(species) %>%
  pull()
```
